% resume.tex
%
% (c) 2011 John Driscoll <johnoliverdriscoll@gmail.com> 
% http://johndriscoll.name
%

\documentclass[11pt]{article}

% Import macros
\usepackage{fullpage}
\usepackage{setspace}
\usepackage{geometry} 
\usepackage{tabulary}
\usepackage{auto-pst-pdf}
\usepackage{pstricks}
\usepackage{pst-barcode}

% Page style
\pagestyle{empty}
\geometry{letterpaper, twoside} 
\setlength{\tabcolsep}{0in}
\setstretch{1}

% Margins
\oddsidemargin  0.0in
\evensidemargin 0.0in
\textwidth      6.5in
\topmargin      0.0in
\headheight     -0.5in
\textheight     9.8in

% Resume
\begin{document}

%% Heading
\noindent
\huge\textbf{John Driscoll}\\\\
{\footnotesize\noindent
  Unix /
  Node.js /
  Coffescript /
  Javascript /
  Express /
  Python /
  Django /
  Ruby on Rails /
  Sinatra /
  jQuery /
  Sencha /
  Raphael /
  MySQL /
  Postgres /
  Mongo /
  Apache /
  Nginx /
  Java /
  PHP
}\\\\
\footnotesize
\begin{tabular*}{7in}{@{\extracolsep{\fill}}lllllllllll}
  \begin{pspicture}(0.25in,0.25in)
    \psbarcode{mailto:johndriscoll@gmail.com}{width=0.25 height=0.25}{qrcode}
  \end{pspicture} &
  \textsl{johnoliverdriscoll@gmail.com} &
  \begin{pspicture}(0.25in,0.25in)
    \psbarcode{http://twitter.com/subdeuxed}{width=0.25 height=0.25}{qrcode}
  \end{pspicture} &
  \textsl{@subdeuxed} & &
  \begin{pspicture}(0.25in,0.25in)
    \psbarcode{http://github.com/johnoliverdriscoll}
              {width=0.25 height=0.25}{qrcode}
  \end{pspicture} &
  \textsl{Git} \\\\
  \begin{pspicture}(0.25in,0.25in)
    \psbarcode{http://johndriscoll.name}{width=0.25 height=0.25}{qrcode}
  \end{pspicture} &
  \textsl{johndriscoll.name} &
  \begin{pspicture}(0.25in,0.25in)
    \psbarcode{TEL:12036859467}{width=0.25 height=0.25}{qrcode}
  \end{pspicture} &
  \textsl{203 685 9467} & &
  \begin{pspicture}(0.25in,0.25in)
    \psbarcode{http://johndriscoll.name/resume.tex}
              {width=0.25 height=0.25}{qrcode}
  \end{pspicture} &
  \textsl{\TeX}
\end{tabular*}\\\\

%% Recent projects
\noindent
\large\textbf{Recent Projects}\\

% Stan.js
\noindent
\begin{pspicture}(0.25in,0.25in)
  \psbarcode{http://github.com/johnoliverdriscoll/stan}{width=0.25 height=0.25}{qrcode}
\end{pspicture}\hspace{0.45in}
\large{Stan.js}\hspace{2.4in}
\textsl{github.com/johnoliverdriscoll/stan}\\
{\small\noindent
Free Javascript library that fixes bugs and missing features for
modern CSS layout support in MSIE versions 5.5, 6, 7 and 8.
}\\

% QTPy
\noindent
\begin{pspicture}(0.25in,0.25in)
  \psbarcode{http://qtpy.mobi}{width=0.25 height=0.25}{qrcode}
\end{pspicture}\hspace{0.45in}
\large{QTPy}\hspace{2.4in}
\textsl{qtyp.mobi \footnotesize{(github.com/johnoliverdriscoll/qtpy)}}\\
{\small\noindent
Created in a week as part of my application to work at reddit.  QTPy is a 
machine-learning strategist and the first Quantum Tic-tac-toe playing bot. 
Implemented in Python for the Google App Engine.  Compatible as a iPhone
native webapp.
}\\

% Smood
\noindent
\begin{pspicture}(0.25in,0.25in)
  \psbarcode{http://smoodui.appspot.com}{width=0.25 height=0.25}{qrcode}
\end{pspicture}\hspace{0.45in}
\large{Smood}\hspace{2.4in}
\textsl{smoodui.appspot.com}\\
{\small\noindent
Freeform, in-browser webpage creator and host.  Coded in Python for the 
Google App Engine and Datastore with tons of Javascript and Ajax for the
user interface.  Layouts created with this service render identically in all 
major layout engines.  Although the editor is only officially supported in
Firefox, Google Chrome support is nearly complete.
}\\

% BBCue
\noindent
\begin{pspicture}(0.25in,0.25in)
  \psbarcode{http://github.com/johnoliverdriscoll/bbcue}{width=0.25 height=0.25}{qrcode}
\end{pspicture}\hspace{0.45in}
\large{BBCue}\hspace{2.4in}
\textsl{github.com/johnoliverdriscoll/bbcue}\\
{\small\noindent
Robust Shell script for burning CDs using CUE data files.  This script aims
to make the backup process of Audio CDs painless by compensating for bugs in 
CUE files generated by bit-perfect CD-ripping applications on all platforms.
}\\

%% Certifications
\noindent
\large\textbf{Certifications}\\

% Java
\noindent
\large{Oracle Certified Professional, Java SE 6 Programmer}\\

%% Experience
\noindent
\large\textbf{Experience}\\

% iSwifter
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
\large{iSwifter} & Menlo Park, CA\\\\[-0.1in]
\textsl{Software Engineer} &
\textsl{\small{November 2011 to Present}}\\
\end{tabular*}\\\\
{\small\noindent
Created real-time usage analytics for cloud-based iOS browser.
Ported video streaming framework from Objective-C/iOS to Java/Android.
Designed and implemented analytics datastore using Mongo and Sinatra.
Designed and implemented Node.js ETL server unflattening Mongo to Postgres
with jQuery and Highcharts dashboard.
}\\\\

% Crumpeta
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
\large{Crumpeta Consulting, LLC.} & Stamford, CT\\\\[-0.1in]
\textsl{Web Developer} &
\textsl{\small{June 2011 to November 2011}}\\
\end{tabular*}\\\\
{\small\noindent
LAMP and Unix administration of development and production server
environments.  Development of subscription-based e-commerce sites using
Drupal and Ubercart.  Module creation including billing, custom registration 
and cross-site reporting.  Creation of real-time, web-based reporting tools
using Sencha Ext.  Implemented A/B split testing for creative conversion
tracking integrating Drupal with custom Node.js and MongoDB driven
application.
}\\\\

% Rampage
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
\large{Rampage Skateparks, LLC.} & Bridgeport, CT\\\\[-0.1in]
\textsl{Social and Mobile Application Developer} & 
\textsl{\small{September 2011 to Present}}
\end{tabular*}\\\\
{\small\noindent
Development of Facebook application with Android and iOS clients integrating 
profiles, multimedia and e-commerce.  Implemented aggregated customer rewards 
program with points collected from online and in-store POS purchases, and
participation in community skateboarding competitions.  Automated 
synchronization of sales data from proprietary Quickbooks POS to remote, free
software database.  Deployment with PhoneGap for mobile cross-platform support.
Self hosted company blog served with Calipso on Node.
}\\\\

% Gartner
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
\large{Gartner Group} & Stamford, CT\\\\[-0.1in]
\textsl{HR Systems Specialist} &
\textsl{\small{March 2009 to November 2009}}\\
\textsl{Systems Analyst} &
\textsl{\small{September 2007 to March 2009}}\\
\end{tabular*}\\\\
{\small\noindent
Created, coded and maintained periodic HR reports.  Tested and customized new 
company job board using Oracle E-Business suite and provided technical
assistance and feedback.  Ruby and VB scripts written to process and tidy data
from multiple sources and formats.
}\\\\

% Advantage
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
\large{Advantage Human Resources} & Stamford, CT\\\\[-0.1in]
\textsl{Administrative Assistant} &
\textsl{\small{May 2007 to September 2007}}\\
\end{tabular*}\\\\
{\small\noindent
Temporary assignments included Child Guidance Center, LLC. and Gartner Group.
}\\\\

\end{document}
